\input{../../templates/harshibar/preamble}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\noindent
\textbf{\LARGE Budi Santoso} \\
\vspace{4pt}
\small +62 XXX XXXX XXXX | \href{mailto:XXX@email.com}{budi.santoso@email.com} | \href{https://linkedin.com/in/xxx}{\myuline{LinkedIn}} | \href{https://github.com/xxx}{\myuline{GitHub}} | \href{https://xxx.dev}{\myuline{Portfolio}}

\vspace{4pt}
\noindent\small{Senior Software Engineer with 5+ years building scalable web applications across fintech, e-commerce, and enterprise sectors. Proven expertise in frontend architecture, performance optimization, and leading cross-functional engineering teams. Passionate about developer experience and delivering high-impact solutions.}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Institut Teknologi Bandung}{Bandung, Indonesia}
      {AI Research Assistant | Python, HuggingFace, OpenAI API, LangChain}{Aug 2022 -- Feb 2024}
      \vspace{2pt}\\
      {\small\textit{AI and Machine Learning Research Lab at School of Electrical Engineering and Informatics.}}
      \resumeItemListStart
        \resumeItem{Published research paper on Indonesian NLP by fine-tuning LLaMA and GPT models for low-resource language tasks using HuggingFace Transformers.}
        \resumeItem{Built RAG-based question answering system achieving 88\% accuracy by integrating OpenAI embeddings with FAISS vector store and LangChain.}
        \resumeItem{Developed prompt engineering framework reducing hallucination rate by 40\% through chain-of-thought and few-shot learning techniques.}
        \resumeItem{Created automated evaluation pipeline for LLM outputs by implementing Python scripts with OpenAI API and HuggingFace datasets.}
      \resumeItemListEnd

    \resumeSubheading
      {Tiket.com}{Jakarta, Indonesia}
      {Senior Frontend Engineer | React, TypeScript, GraphQL, Node.js}{Mar 2024 -- Present}
      \vspace{2pt}\\
      {\small\textit{Indonesia's leading online travel and entertainment booking platform.}}
      \resumeItemListStart
        \resumeItem{Reduced booking flow load time by 35\% by redesigning the page loading pipeline using React Suspense and lazy loading patterns.}
        \resumeItem{Architected a micro-frontend system serving 5M+ monthly users by implementing Module Federation with Webpack 5 and React.}
        \resumeItem{Decreased API response handling time by 40\% by migrating REST endpoints to GraphQL with Apollo Client.}
        \resumeItem{Improved mobile web performance score from 45 to 85 by implementing code splitting, lazy loading, and image optimization strategies.}
        \resumeItem{Established frontend testing culture achieving 70\% coverage by introducing Jest unit tests and Cypress E2E automation.}
      \resumeItemListEnd

    \resumeSubheading
      {Bukalapak}{Jakarta, Indonesia}
      {Software Engineer, Frontend | Next.js, React, TypeScript, Redis}{Jan 2021 -- Jul 2022}
      \vspace{2pt}\\
      {\small\textit{One of Indonesia's leading e-commerce marketplaces and digital payment platforms.}}
      \resumeItemListStart
        \resumeItem{Boosted search page load speed by 55\% by implementing server-side rendering with Next.js.}
        \resumeItem{Increased seller dashboard adoption by 30\% by leading a team of 3 engineers to rebuild the interface using React and TypeScript.}
        \resumeItem{Reduced production bugs by 60\% by championing TypeScript strict mode adoption across 12 frontend repositories.}
        \resumeItem{Automated 8 manual deployment processes by building CI/CD pipelines using GitHub Actions and Docker.}
        \resumeItem{Mentored 4 junior developers through pair programming sessions, resulting in 2 promotions within the team.}
      \resumeItemListEnd

    \resumeSubheading
      {Mekari}{Jakarta, Indonesia}
      {Frontend Developer | Vue.js, Nuxt.js, TypeScript, Storybook}{Feb 2020 -- Dec 2020}
      \vspace{2pt}\\
      {\small\textit{HR and accounting SaaS platform for SMEs.}}
      \resumeItemListStart
        \resumeItem{Accelerated feature delivery by 35\% by building a shared component library with 50+ reusable components using Vue.js and Storybook.}
        \resumeItem{Reduced customer support tickets by 25\% by redesigning the onboarding flow based on user research and analytics data.}
        \resumeItem{Improved developer onboarding time from 2 weeks to 3 days by creating comprehensive documentation and coding standards.}
        \resumeItem{Migrated legacy jQuery codebase to Vue.js, eliminating 15K lines of technical debt and improving maintainability.}
      \resumeItemListEnd

    \resumeSubheading
      {Xtremax}{Bandung, Indonesia}
      {Junior Frontend Developer | React, JavaScript, SASS, Webpack}{Jun 2019 -- Jan 2020}
      \vspace{2pt}\\
      {\small\textit{Regional digital agency specializing in web and mobile applications for government and enterprise clients.}}
      \resumeItemListStart
        \resumeItem{Delivered 6 client projects on time by developing responsive web applications using React and SASS.}
        \resumeItem{Reduced bundle size by 45\% by configuring Webpack code splitting and tree shaking for production builds.}
        \resumeItem{Improved website accessibility scores to WCAG AA compliance by implementing semantic HTML and ARIA attributes.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance}{Remote, Indonesia}
      {Web Developer | HTML, CSS, JavaScript, WordPress}{Jan 2018 -- May 2019}
      \vspace{2pt}\\
      {\small\textit{Independent freelance web development.}}
      \resumeItemListStart
        \resumeItem{Completed 12 freelance projects with 5-star ratings by delivering custom WordPress themes and landing pages.}
        \resumeItem{Generated Rp 50M+ in client revenue by building e-commerce websites with WooCommerce integration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section {Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Institut Teknologi Bandung}{2022 -- 2024}
      {M.Kom. Computer Science (3.85/4.00)}{Indonesia}
    \resumeSubheading
      {Universitas Padjadjaran}{2014 -- 2018}
      {S.Kom. Informatics (3.65/4.00)}{Indonesia}
  \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
     \textbf{Languages:} Python, TypeScript, JavaScript \\
     \textbf{AI/ML:} LangChain, OpenAI API, HuggingFace, RAG, Prompt Engineering, FAISS \\
     \textbf{Backend:} Node.js, Express.js, GraphQL, REST APIs \\
     \textbf{Frontend:} React.js, Next.js, Vue.js, Nuxt.js \\
     \textbf{DevOps:} Docker, Kubernetes, AWS, GCP, GitHub Actions, Jenkins \\
     \textbf{Databases:} PostgreSQL, MongoDB, Redis \\
     \textbf{Testing:} Jest, Cypress, Playwright, React Testing Library \\
     \textbf{Tools:} Git, Webpack, Vite, Figma, Jira \\
     \textbf{Methodologies:} Agile, Scrum, CI/CD, TDD, Code Review
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
